Language Bias in a Multilingual Tweet Corpus

### 2018-06-25 paper.tex
More topics

To study the collection in more detail, we manually searched the collection for \hl{9} topics of interest.

@@

To investigate the collection further, \hl{nine} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
\begin{itemize}
\item \texttt{LV001: Winter} Everything about winter.
\item \texttt{LV002: 
The Chronicles of Melanie} Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for Foreign-Language Category for Oscars.
\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004: Blizzard of Souls} A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is currently in production.
\item \texttt{LV005: Ice hockey} Ice hockey related tweets.
\item \texttt{LV006: Christmas} Christmas.
\item \texttt{LV007: New Year} New Year.
\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
\item \texttt{LV009: Brexit} Brexit.
\end{itemize}

>>>>

To study the collection in more detail, we manually searched the collection for \hl{16} topics of interest.

@@

To investigate the collection further, \hl{16} topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are:
\begin{itemize}
\item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
\item \texttt{LV005:} \textbf{Ice hockey} \ Ice hockey.
\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
\item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
\item \texttt{LV015:} \textbf{May 4} \ The Restoration of Independence Day.
\item \texttt{LV011:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8). It is also honored as the Victory Day on May 9. The Europe Day is observed on May 9. Tweets about any of the three events are relevant.
\item \texttt{LV010:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
\item \texttt{LV014:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
\item \texttt{LV013:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
\item \texttt{LV006:} \textbf{Christmas} \ Christmas.
\item \texttt{LV007:} \textbf{New Year} \ New Year.
\item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
\end{itemize}
